Flabby and injective objects in toposes

### 2018-10-21 paper-flabby-objects.tex
Applications of the internal characterization

>>>>

The internal characterization provided by
Theorem~\ref{thm:higher-direct-images-as-internal-sheaf-cohomology} gives, as a
simple application, a geometric explanation that higher direct images along
the identity~$\mathrm{id} : X \to X$ vanish: From the internal point of view
of~$\Sh(X)$, the over-locale~$X$ corresponds to the one-point locale, and the
higher cohomology of the one-point locale vanishes.

In algebraic geometry, the internal characterization can be used to immediately
deduce the explicit description of the higher direct images of Serre's twisting
sheaves along the projection~$\mathbb{P}^n_S \to S$, where~$S$ is an arbitrary
base scheme (or even base locally ringed locale), from a computation of the
cohomology of projective~$n$-space. Background on carrying out scheme
theory internally to a topos, is given in~\cite[Section~12]{blechschmidt:phd}.
